data_cleaning_longer_period

### 2023-08-29 code/analysis_Redo.Rmd
looking at TMSIS only sample, really
intensity and complexity

@@

@@

summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))
```

>>>>

df.core <- dfc %>% 
  mutate( MCD = Total * Pct.MCD / 100,
         None = Total * Pct.None / 100,
         MCR = Total * Pct.MCR / 100,
         COM = Total * Pct.COM / 100,

@@

## Panel Complexity and Intensity of Care
```{r}

df.select.stint <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100,

         pap.denom = pap.denom / Total * 100, 
         crc.denom = crc.denom / Total * 100, 
         adultbmi.denom = adultbmi.denom / Total * 100, 
         childbmi.denom = childbmi.denom / Total * 100, 
         htn.denom = htn.total / Total * 100, 
         dm.denom = dm.total / Total * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5)

did.select.stint <- c(0, 0, 0, 0)

for (j in 10:29){

  df.temp <- df.select.stint[,c(1:9, j, 30:ncol(df.select.stint))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.select.stint <- rbind(did.select.stint, outcomes$coeftable)
}

did.select.stint <- did.select.stint[-1,]
rownames(did.select.stint) <- NULL

p <- df.select.stint %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(HIV.prev:dm.denom) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = HIV.prev:dm.denom) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.select.stint, group =   gsub(x = df.select.stint %>% 
  select(HIV.prev:dm.denom) %>% 
  colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
  arrange(desc(group)) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

p

did2s(
      data = df.select.stint  , 
      yname = "Complexity", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )

did2s(
      data = df.select.stint  , 
      yname = "Intensity", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )

@@

summary(lm(log(Density.Origin) ~ log(Density.NewZip), data = df.z.dist.plot))

df.z.dist.plot %>% 
  arrange(desc(DistToClosestSite))
```

### 2023-08-29 code/data_cleaning_longer.Rmd
intensity and complexity

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:FIPS, Total:Pct.COM, imm.rate:MinYear)

>>>>

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>% 
                mutate(HIV.prev = T6A_L1AND2_CB / Total * 100, 
         HIV.care = T6A_L1AND2_CA / T6A_L1AND2_CB,

         HepC.prev = T6A_L4B_CB / Total * 100,
         HepC.care = T6A_L4B_CA / T6A_L4B_CB,

         Asthma.prev = T6A_L5_CB / Total * 100,
         Asthma.care = T6A_L5_CA / T6A_L5_CB,

         # AbnormalPap.prev = T6A_L8_CB / Total * 100,
         # AbnormalPap.care = T6A_L8_CA / T6A_L8_CB,
         #
         # ImmunizationsGiven.prev = T6A_L24_CB / Total * 100,
         # ImmunizationsGiven.care = T6A_L24_CA / T6A_L24_CB,

         HeartDisease.prev = T6A_L10_CB / Total * 100, 
         HeartDisease.care = T6A_L10_CA / T6A_L10_CB,

         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,

         Depression.prev = T6A_L19A_CB / Total * 100, 
         Depression.care = T6A_L19A_CA / T6A_L19A_CB,

         Diabetes.prev = T6A_L9_CB / Total * 100, 
         Diabetes.care = T6A_L9_CA / T6A_L9_CB,

         Hypertension.prev = T6A_L11_CB / Total * 100, 
         Hypertension.care = T6A_L11_CA / T6A_L11_CB) %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:FIPS, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)
